### 2021-02-21 math/ia_2021/paper.tex
python fixes, features, tex

\subsection{Cleaning the dataset}

The dataset, \cite{noaa}

@@

\subsection{Ease of access of data}
For an easy access to the predictions generated by the program, I implemented 
a simple function to fetch new earthquake events from the \url{https://earthquake.usgs.gov/earthquakes/feed/v1.0/geojson.php} 
live earthquake feed. These earthquake events are quantified into a magnitude \verb|mag| 
and a distance \verb|dist| variable, which are supplied to the statistical model. 
This information is then easily accessible from a human-readable report exported 
to a plaintext file.

@@

This method, like any other statistical approximation, is by no means perfect 
and for that reason should not be used in any real-world application. The results 
procured by the program

>>>>

\subsection{Processing the dataset for use}

The dataset, procured from the NOAA website \cite{noaa}, includes many tsunami 
runups, going back before the year 0. Due to this, the NOAA states uncertainties 
that can occur in its data. For example, reports that were recorded before the 
20th century tend to be based on written accounts, and not recorded seismic activity. 
Furthermore, the installation of a system called the Worldwide Standardized Seismograph 
Network in the 1960s allowed for more accurate data and for that reason any recorded 
activity before this date will be discarded from the dataset.

\dots

The data must be correctly split into a training and an test dataset. The training 
dataset will be used to generate a regression model while the test dataset will 
be used to calculate the general accuracy of the model, by predicting values and 
comparing those to the known value as found in the dataset. The dataset is split based on 
a decimal number using the \verb|df.sample| method found in the Pandas library. A split 
of 70\% for training and 30\% for test has been chosen. A \verb|random_state| argument is 
set to an arbitrary value 42, as if it weren't, the dataset would be split in a different 
manner at each execution of the program.

@@

Regression analysis is a very large portion of statistics, and regression models can 
be found in numerous use cases of the field. Regression models consist of estimating the 
relationship between one (or more) independent variables and a dependent variable. A 
simple example of regression can be seen in the linear relationship between for example

\dots

The model's accuracy is then calculated, with the mentioned before "test" dataset. 
The \verb|accuracy_score| method from the \verb|sklearn.metrics| class is used for this 
task.

\subsection{Ease of access}
For an easy access to the predictions generated by the program, I implemented 
a simple function to fetch new earthquake events from the \url{https://earthquake.usgs.gov/earthquakes/feed/v1.0/geojson.php} 
live earthquake feed. These earthquake events are quantified into a magnitude \verb|mag| 
and a distance \verb|dist| variable, which are supplied to the statistical model. 
This information is then easily accessible from a human-readable report exported 
to a plaintext file. Following is an example report generated by the tool:

@@

This method, like any other statistical approximation, is by no means perfect 
and for that reason should not be used in any real-world application. The results 
procured by the program are subject to many
